Multi-level modelling with Openflexo/FML - A contribution to the \mpc

### 2021-05-25 6-ModelPresentation.tex
Updates from Overleaf

\begin{lstlisting}[breaklines=true, language=java, basicstyle=\ttfamily\scriptsize, mathescape=true]
forEach (artifactType : types) {
    assert !(artifactType instanceof CodeArtifactType) | artifactType.isSenior
}
\end{lstlisting}

>>>>

\begin{lstlisting}[breaklines=true, language=java, basicstyle=\ttfamily\scriptsize, mathescape=true]
forEach (artifactType : types) {
    assert !(artifactType instanceof CodeArtifactType) | artifactType.implements(programmingLanguages)
}
\end{lstlisting}
